Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce

### 2019-09-20 Paper.tex
dsadsadas

Both academic literature and daily experience shows that \textit{arbitrary faults} frequently occur corrupting our results \cite{BFLMapReduce}. Moreover, ignore data-set locality can lead to performance degradation and a pointless bigger network traffic \cite{LARTS}.

In this paper we present an original MapReduce runtime system capable both to tolerate arbitrary faults and to recognize input data network locations and sizes in order to perform a \textit{locality-aware task scheduling}, improving performance and diminishing network traffic.

Although job's execution using our system requires more resources respect to other implementations, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
\end{abstract}

@@

Therefore to construct a distributed system capable to provide its services even in the presence of failures, that is to design a \textit{fault tolerant} cloud application, is a critical aspect of software engineering.

Moreover, due to very large data-set involved during data-intensive tasks, exploiting data locality becomes crucial aspect in order to mitigate network traffic and delay, improving so performance.

In these paper we will describe an \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) MapReduce system which is capable to resolve all issues described above.

Our AFTLA MapReduce prototype, which is capable to perform a word-count by a given text input file, is been implemented from scratch using Go programming language using some external libraries, including those necessary to interact with an Apache ZooKeeper\textsuperscript{TM} cluster\footnote{\url{https://zookeeper.apache.org}}, which we have adopt for system's coordination purposes, and with Amazon AWS services, because we have adopt Amazon S3 for storage; note that all libraries used in our prototype are fully described in table \ref{tab:libraries}.

Our prototype is been design to run into several Amazon EC2 instances hosted in a same region (\texttt{us-east-1})\footnote{Note that, due to Account AWS Educate Starter limitations, we could not run Amazon EC2 instances on other regions.}, adopting AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} to associate some of our EC2 instance to an public IPv4 address in order to enable communication with the internet and then to connect a local computer to our system.

@@

\section{Assumptions}

In order to properly describe how our system can achieve a certain level of arbitrary fault tolerance without unduly compromising performance, let's start making some very important assumptions.

We have designed our cloud application as a \textit{set of processes}, every of which have to run on \textit{different} servers with a certain replication degree in order to achieve a certain level of arbitrary fault tolerance. Available processes are not all the same but several kind of these exist with its own features and aims which we will describe them in detail in following section; in fact, we distinguish three process type: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);

We assume that all processes are connected by \textit{reliable channels}, that is no messages are lost, duplicated or corrupted. In our prototype that feature is guaranteed  by the use of Go implementation of RPC\footnote{\url{https://golang.org/pkg/net/rpc/}} (\textit{Remote Procedure Call}) which is based on TCP connections. Mostly all RPC calls, except those made by the client process, are asynchronous\footnote{Although Go's \texttt{rpc} package provides its own support for RPC asynchronous calls, we have  preferred to adopt an equivalent approach based on properly used goroutine and channels.}.

Clients are \textit{always correct}, because if they are not there is no point in worrying about the correctness of our system's output. Finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.

@@

As you can see from figure \ref{fig:model}, our system is made up of several kinds of processes each of which has its own features and purposes.

@@

It can interact with system's key-value storage service (i.e. DFS or an equivalently cloud key-value storage service) for job's input uploading and job's output downloading using HTTP-based RESTful APIs, according to which both an URL and the use of standard HTTP methods (\texttt{GET} and \texttt{PUT}) only are required in order to perform data transmission between our cloud system and client

Is very important to specify that, in our system, URLs are provided by current leader primary process (CLPP) for security and compatibility reasons with some cloud storage services. In fact, unlike Hadoop, which use HDFS (\textit{Hadoop Distributed File System}) to store input and output data, our prototype adopts Amazon S3 for data storage purposes. According to Amazon S3 implementation, since all objects and directories (latter are called \textit{buckets}) are by default private, clients cannot upload or download data without AWS security credentials or permissions.

Therefore, rather than distribute AWS security credentials which can imply huge security risks, we have adopt a design according to which client processes have to request special URLs to CLPP to accomplish their data transmissions; these kind of URLs are called \textit{pre-signed URLs}. According to Amazon AWS documentation, anyone who receives a valid pre-signed URL can upload (or download) an object from Amazon S3. However only someone that has a valid security credentials can create a pre-signed URL; this is the reason according to which CLPP, which has AWS security credentials to interact with Amazon S3\footnote{We remember that to give all privileges required for pre-signed URL creation to the EC2 instances where CLPP are running, we have to properly set all necessary IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}, has to generate and distribute them to clients.

However clients process are unaware of CLPP network location which, as we will see in the next paragraph, can change during system activities due to either a crash or connectivity lost. To be more precise any system's process know network location of the others although Zookeeper cluster location, which we have adopt for membership managing and coordination purposes, must be known by everyone; therefore we can state that location transparency of our application is only partial.

Since, as we will see, is possible to know network location of a specified process querying Zookeeper cluster, clients are able to know where CLPP is both to require pre-signed URL and to submit jobs.

@@

Most of the activities carried out by a Primary Process (PP) are very similar to those performed by \textit{JobTracker} process used in Apache Hadoop framework. These activities including \textit{Map-Task} or \textit{Reduce-Task} scheduling, pre-signed URLs generation, managing of worker nodes replies, clients request managing and so on.

However unlike Apache Hadoop framework, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}. Therefore, to ensure an high system availability, inspired by Apache Mesos\textsuperscript{TM}\ architecture\footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, we have adopt a design according to which multiple PP backup copies exist and they run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by. Using this approach, is possible to manage PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.

, only LPP can interact with WPs and modify data into the Zookeeper Cluster. Note that LPP schedules several task using a \textit{push-based} approach (unlike Hadoop according to which JobTracker schedules task using a \textit{pull-based} approach \cite{LARTS})

However, to perform its task, LPP manages various information about clients requests, many of which, as we will see later, are sent by WP after a map or reduce task. In other word, LPP has got a status.

@@

Therefore we have adopt a design according to which LPP make a sort of backup, or snapshot, of its current state regularly. To make our implementation easier, in our prototype, considering that LPP state contains a very small amount of data, LPP stores its state in a Zookeeper cluster after some events, like a map task termination. In case of crash failure of current LPP, when a primary process backup becomes leader, it retrieves all data from Apache ZooKeeper cluster, recovering last saved state.

@@

To make WP arbitrary fault-tolerant we have adopt a design according to which each task (map, reduce, etc.) is executed more than once by different processes running on different host. This approach requires to organize all our WPs into several \textit{groups} through which became possible to mask one or more faulty processes of a given group.

Before explaining how we manage WP faults, we must explain what is a Worker Processes Group (WPG). A WPG is a set of identical worker processes, each of which execute, relatively to a given job, \textit{the same commands using the same input data in the same order}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs. All commands and data are sent by LPP.

Suppose to want tolerate at most $f$ arbitrary failures of all WPs belonging to a given group.

To achieve that level of fault-tolerance, we can apply to reach, for instance, \textit{byzantine agreement} among all processes belonging to group. However we believe that solution is too expensive because it requires, as properly explain in literature\citep{SDCC}, $3f + 1$ replicas.

@@

In our design each map or reduce task scheduled by current LPP are assigned to independent WPGs. Let's try to explain this statement formally using map task as example (but is the same of any task). Let $i = 1,2,3...n$, where $n \in \mathbb{Z}_+$. As MapReduce framework states, our system splits the input text file $S$ in $n$ parts $\lbrace s_1, s_2, ... s_n \rbrace$ called \textit{split}; each split $s_i$ is associated to a map task $m_i \in \lbrace m_1, m_2, ... m_n \rbrace$ every of which must be replicated on multiple WPs to make them arbitrary fault tolerant. Each map task $m_i$ is assigned to a different WPG $g_i \in \lbrace g_1, g_2, ... g_n \rbrace$. As we will explain later, LPP, checking received outputs from each group, we can achieve arbitrary fault tolerance for every scheduled task. Obliviously to tolerate at most $f$ arbitrary failures of each task, each WPG must contains at least $2f+1$ different processes. Then our design requires at least $n(2f+1)$ different WPs.

This design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs. If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG, increasing the number PP backups too.

@@

Given the system model described previously, a solution to tolerate at most $f$ arbitrary faults during each task would be the following: current LPP assigns a given map/reduce task to a WPG contacting its $2f + 1$ WPs; then, after retrieving the outputs from replicas, picks the most voted results which is expected correct if no more than $f$ arbitrary faults occur.

This simplistic solution is very expensive because it replicates everything $2f + 1$ times: task execution, communication of map task outputs and so on. We use a set of techniques to avoid these costs and do things efficiently:

\subsection{Digest outputs} As explained above, in order to consider a map/reduce task correct, tolerating at most $f$ faulty processes, $f + 1$ matching outputs, coming from at least $2f + 1$ WPs belonging to a given WPG,  have to be received.

To validate task's output, since outputs computed by worker processes can be very large, in order to avoid pointless additional network traffic, we have adopted an approach according to which LPP fetches and compares \textit{digests}, a bit string of a fixed size obtained using a hash function. The main advantage of this technique is that, digest size are many times smaller than task's data output, allowing us to reduce network traffic among servers, increasing system's performance.

\subsection{Locality-Aware Deferred Execution}

Waiting for $2f + 1$ matching replies during a AFT Map-Task can be a waste of time especially when no faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ Map-Task for each AFT Map-Task.

Therefore, to minimize both the number of Map-Task executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware Deferred Execution}.

According to that solution, during a AFT Map-Task execution, only $f + 1$ Map-Task replicas are started checking if they all return the same result. If a time-out elapses or some return results do not match, more Map-Task replicas (up to $f$) are started, until we obtain $f + 1$ matching replies. When faults are unlikely, this approach, which we believe to be energy-saver\footnote{Assuming that idle WPs consume less energy respect to non-idle WPs, minimize the number of Map-Task executed involves minimize the amount of electricity used.}, is capable to minimize the number of WPs involved into computations respect to basic scheme, improving overall system performance.

Moreover, this mechanism can reduce overall system response time because it is designed to minimize data transfer time too. When an AFT Map-Task starts $f + 1$ Map-Task replica on WPs, the latter are not chosen at random but according to their network location; in fact, Map-Task are scheduled firstly to the $f + 1$ nearest nodes giving priority to them. Only when we can't get $f + 1$ matching replies, the most distant nodes are used. The most difficult problem consists into determine WP's network location considering the variation of network traffic. In literature, many network proximity evaluation's methods exist which can be static (i.e. hop number) or dynamic (round-trip time evaluation, HTTP request emulation, etc.); in our prototype, we have adopt a very simple network proximity evaluation's method based on \texttt{ping} which able us to evaluate round-trip time among system's nodes.

@@

Although the advantages of the locality-aware deferred execution mechanism, we believe that waiting for $f + 1$ matching Map-Task for every AFT Map-Task results before starting the Reduce-Phase can worsen the time for the job completion, especially when WPs arbitrary failures are uncommon. Formally, assuming that we have $n$ WPG, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies; all Map-Phase may require long time especially when network traffic or data set size are huge.

A way to increase system's performance reducing its response time is the following: when all scheduled AFT Map-Tasks have received the \textit{first} Map-Task result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finish. Essentially, our system make a bet according to which arbitrary faults are highly unlikely therefore first Map-Task replies are considered as correct. This mechanism is called \textit{Speculative Execution}.

Obviously validate the correctness of first Map-Task replies is critical otherwise job's output can be incorrect. In order to do that, all AFT Map-Tasks keep on waiting their $f + 1$ matching replies even when Reduce-Phase is started. When Map-Phase is fully finish, if is detected that the input used in the Reduce-Phase was not correct, Reduce-Phase will be restarted with the correct input, otherwise we can finish our job in much less time.

@@

\subsection{Data Locality-Aware Reduce Scheduling}

Since in order to achieve fault tolerance we have replicate all task $2f + 1$ times, data transfers among servers are replicated too, generating an huge amount of network traffic. Evidently, when large data set are involved, move data repeatedly among server became a bottleneck.

Therefore we have adopted a design aware of data locations and sizes capable to reduce the overall amount of transferred data; that solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}"; in other words  "\textit{moving computation towards data is cheaper than moving data towards computation}".

To be more precise, when a WP complete a map task, it send as output to LPP two very important information: a string containing data output digest and a value representing output data size. According to Hadoop terminology, map task output are called \textit{partition} and, contrary to splits, they are of variable sizes: so why not just shuffle smaller partitions instead big one?

Assume for simplicity that no faults occurs and to have only two WPGs $\lbrace g_1, g_2 \rbrace$. Let $P_{i:g_i}$ the partition owned by WPG $g_i$ which contains all key-value pairs which must be submitted to reduce task $R_i$. The problem is how to perform a locality-aware reduce task scheduling; in other word, which WPG $g_i$ have to run reduce task $R_i$ reducing shuffled data?

Suppose that $P_{1:g_1}$, $P_{2:g_1}$, $P_{1:g_2}$ and $P_{2:g_2}$ have a size of 300 MB, 150 MB, 150 MB and 300 MB respectively. Clearly, scheduling $R_1$ at $g_1$ and $R_2$ at $g_2$ reduce the amount of transferred data among WPGs by 50\%. Obliviously using this approach is possible to perform a locality-aware shuffle task capable to reduce network traffic, applying locality to reduce task scheduling.

>>>>

Both academic literature and daily experience shows that \textit{arbitrary faults} frequently occur corrupting our results \cite{BFLMapReduce}. Moreover, ignore \textit{data-set locality} can lead to performance degradation and a pointless bigger network traffic \cite{LARTS}.

In this paper we present a MapReduce runtime system as a solution to these problems. Although job's execution using our system requires more resources respect to other implementations due to process replications, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
\end{abstract}

@@

For these reasons, to construct a distributed system capable to provide its services even in the presence of failures, mitigating network traffic and delay, is become a critical aspect of software engineering.

In these paper we will describe an \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFT-LA) MapReduce system capable to resolve all issues described above.

\section{Assumptions and remark}

In order to properly describe how our system can achieve a certain level of arbitrary fault tolerance without unduly compromising performance, let's start making some very important assumptions and observations.

We have designed our cloud application as a \textit{set of processes}, every of which have to both run on \textit{different} servers and have got a certain replication degree in order to achieve a certain level of arbitrary fault tolerance, therefore we have deploy our processes in several Amazon EC2 instances hosted in a same region (\texttt{us-east-1})\footnote{Note that, due to Account AWS Educate Starter limitations, we couldn't run Amazon EC2 instances on other regions.}.

In order to enable communication with the Internet and therefore allow a local computer to connect to our system, we have adopt AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} which able us to associate to some of our EC2 instance to a public static IPv4 addresses\footnote{Public IPv4 addresses associated to any EC2 instances by default change after every start. Therefore, if an Amazon EC2 crashed and have to be restarted, client wouldn't able to connect to it due to address change.}.

Observe that processes are not all the same but several kind of these exist, with its own features and aims: although we will describe them in detail in following section, just note that we distinguish three process type: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);

Note that our MapReduce system is been implemented to execute word-count job only. We have built our system from scratch using Go programming language\footnote{\url{https://golang.org}} using some external libraries, which are all reported in table \ref{tab:libraries}.

All processes are connected by \textit{reliable channels}, that is no messages are lost, duplicated or corrupted. In our prototype that feature is guaranteed  by the use of Go implementation of RPC\footnote{\url{https://golang.org/pkg/net/rpc/}} (\textit{Remote Procedure Call}) which is based on TCP connections. Mostly all RPC calls, except those made by the client process, are asynchronous\footnote{Although Go's \texttt{rpc} package provides its own support for RPC asynchronous calls, we have  preferred to adopt an equivalent approach based on properly used goroutine and channels.}.

Clients are \textit{always correct}, because if they are not there is no point in worrying about the correctness of our system's output. We assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.

@@

@@

Let's start now the analysis of all processes of our system.

@@

It can interact with system's key-value storage service (i.e. DFS or an equivalently cloud key-value storage service) for job's input uploading and job's output downloading. To perform data transmissions, client processes use HTTP-based RESTful APIs, according to which both an URL and standard HTTP methods (\texttt{GET} and \texttt{PUT}) only are required.

Is very important to specify that, in our system, URLs are provided by a PP for security and compatibility reasons with some cloud storage services. In fact, unlike Hadoop, which use HDFS (\textit{Hadoop Distributed File System}) to store input and output data, our prototype adopts Amazon S3 for data storage purposes. According to Amazon S3 implementation, since all objects and directories (\textit{buckets}) are by default private, clients cannot upload or download data without AWS security credentials or permissions.

Therefore, rather than distribute AWS security credentials which can imply huge security risks, we have adopt a design according to which client processes have to request special URLs to PP to accomplish their data transmissions; these kind of URLs are called \textit{pre-signed URLs}. According to Amazon AWS documentation, anyone who receives a valid pre-signed URL can upload (or download) an object from Amazon S3. However only someone that has a valid security credentials can create a pre-signed URL; this is the reason according to which PP, that has AWS security credentials to interact with Amazon S3\footnote{We remember that to give all privileges required for pre-signed URL creation to the EC2 instances where PP is running, we have to properly set all necessary IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}, has to generate and distribute them to clients.

Observe that client processes are unaware of PP network location, that is they doesn't know its internet address (which can change during system activities due to either a crash or connectivity lost because to Amazon EC2 policies). To be more precise any system's process know network location of the others although an Apache Zookeeper\textsuperscript{TM}\ cluster location, which we have adopt for membership managing and coordination purposes, must be known by everyone. According to our design, is possible to know network location of a specified process querying Zookeeper cluster, therefore clients are able to know where PP is and then it can both require pre-signed URL and submit jobs.

@@

Most of the activities carried out by a Primary Process are very similar to those performed by \textit{JobTracker} process used in Apache Hadoop framework. These activities including \textit{Map-Task} or \textit{Reduce-Task} scheduling, pre-signed URLs generation, managing of worker nodes replies, clients request managing and so on.

However unlike Apache Hadoop framework, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}. Therefore, to ensure an high system availability, inspired by Apache Mesos\textsuperscript{TM}\ architecture\footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, we have adopt a design according to which multiple PP backup copies exist and they run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by. Using this approach, is possible to manage a PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.

@@

Therefore we have adopt a design according to which LPP save its state regularly. Since LPP state consists on a very small amount of data, we have design LPP to store its state into Apache Zookeeper cluster upon the occurrence of certain events. When a LPP crash failure occurs, the new leader can easily retrieves last saved state from  ZooKeeper cluster. Note that Apache Zookeeper's processes is been replicated too in order to tolerate a certain number of faults upon Zookeeper cluster.

Another difference Hadoop \textit{JobTracker} process regards task scheduling approach. In our design LPP schedules tasks to WP using a \textit{push-based} approach, contrariwise Hadoop JobTracker schedules task using a \textit{pull-based} approach where WP ask for tasks\cite{LARTS}.

@@

To achieve fault tolerance we have adopt a design according to which each task is executed more than once by different processes running on different host. To do this, as you can see from figure \ref{fig:model}, we have adopt a design according to which all worker processes are organized in several groups which we have used to mask one or more faulty processes: these groups are called \textit{Worker Processes Group} (WPG). To be more precise, an WPG is a set of identical WP, each of which execute \textit{the same commands using the same input data in the same order}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs.

According to our system's design, any word-count job is made up of two main phases: \textit{Map-Phase} and \textit{Reduce-Phase}. To fully complete the Map-Phase of a job is necessary to successfully perform a certain number of special tasks called \textit{Arbitrary Fault-Tolerant Map-Tasks} (\textit{AFT-Map Tasks}): a AFT-Map represents a fault tolerant version of classical map task, in fact it simply consist on a replicated map task among a certain number of WP. To be more precise, our system is been design so that each WPG performs its own AFT-Map Task independently: to do that, each WPs, belonging to a given WPG, will perform the same map task in order to mask faulty processes. Clearly all this is also valid for Reduce-Phase.

Suppose now to want tolerate at most $f$ arbitrary failures. To achieve that level of fault-tolerance is clearly necessary that any AFT-Map Task or AFT-Reduce Task assigned to each WPG are able to tolerate at most $f$ arbitrary failures. At this point we can apply, for instance, \textit{byzantine agreement} among all processes of a given WPG, but we believe that solution is too expensive because it requires, as properly explain in literature\citep{SDCC}, $3f + 1$ replicas.

@@

Formally, let $i = 1,2,3...n$, where $n \in \mathbb{Z}_+$. LPP splits the input text file $S$ in $n$ parts $\lbrace s_1, s_2, ... s_n \rbrace$ called \textit{splits}; each split $s_i$ is associated to an AFT-Map Task $m_i \in \lbrace m_1, m_2, ... m_n \rbrace$. Each AFT-Map Task $m_i$ is assigned to WPG $g_i \in \lbrace g_1, g_2, ... g_n \rbrace$. Then $2f+1$ different WPs belonging to WPG $g_i$ perform the same map task replica. LPP, checking received outputs from each WP of each group, picks the most voted results which is expected correct if no more than $f$ arbitrary faults occur. Obviously Reduce-Phase is performed in similar ways.

Clearly, this design require more resources respect to classic MapReduce scheme: to tolerate at most $f$ arbitrary failures, each WPG have to contains at least $2f+1$ different WPs, therefore a total of $n(2f+1)$ different WPs are required (to which is also added a certain number of PPs run on different machine).

Although its very high costs, this design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs. If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG (increasing the number of PP backups too).

@@

At this point high costs of this solution should be clear to reader because everything is replicated $2f + 1$ times as map/reduce task, data transmissions and so on. Can we have a good level of fault tolerance without worsening performance? How can we do AFT-Map Task and AFT-Reduce Task efficiently?

In this section we will explain a set of solutions and techniques which we have adopt in our system to reduce costs and do things efficiently:

\subsection{Digest outputs} As explained above, in order to consider any AFT-Map Task/AFT-Reduce Task correct, tolerating at most $f$ faulty processes, $f + 1$ matching outputs, coming from at least $2f + 1$ WPs belonging to a given WPG to which we have assign the aforementioned task, have to be received.

Since outputs computed by WPs can be very large, we have adopted an approach according to which, instead of to compare raw data, LPP fetches and compares \textit{digests} that is fixed size strings obtained from WPs outputs using an hash function. The main advantage of this technique is that digest size are many times smaller than task's data output, allowing us to validate task's output reducing network traffic among servers.

\subsection{Locality-And-State-Aware Deferred Execution}

Waiting for $2f + 1$ matching replies during any AFT Map-Task/AFT-Reduce Task can be a waste of time especially when no faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ replicas for a given AFT-Map Task/AFT-Reduce Task.

Therefore, to minimize both the number of replicas executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware Deferred Execution}.

According to that solution, during a AFT Map-Task/AFT-Reduce Task execution, only $f + 1$ replicas are started checking if they all return the same result. If a time-out elapses or some return results do not match, more replicas (up to $f$) are started, until we obtain $f + 1$ matching replies. When faults are unlikely, this approach, which we believe to be energy-saver\footnote{Assuming that idle WPs consume less energy respect to non-idle WPs, minimize the number of Map-Task executed involves minimize the amount of electricity used.}, is capable to minimize the number of WPs involved into computations respect to basic scheme, improving overall system performance.

Moreover, this mechanism can reduce overall system response time because it is designed to minimize data transfer time too because our scheduler gives priority to \textit{nearest} WPs. When an AFT-Map Task/AFT-Reduce Task starts $f + 1$ replica on WPs, the latter are not chosen at random but according to their network location; in fact, the tasks are scheduled firstly to the $f + 1$ nearest nodes. Only when we can't get $f + 1$ matching replies, the most distant nodes are used. The most difficult problem consists into determine WP's network location considering the variation of network traffic. In literature, many network proximity evaluation's methods exist which can be static (i.e. hop number) or dynamic (round-trip time evaluation, HTTP request emulation, etc.); in our prototype, we have adopt a very simple network proximity evaluation's method based on \texttt{ping} which able us to evaluate round-trip time among system's nodes.

We have designed our task scheduler to be also \textit{state-aware} since priority is given to those WPs whit minimum CPU utilization which we compute using \texttt{mpstat} tool. WP's state is acquired indirectly by LPP through their replies.

@@

Although the advantages of the deferred execution mechanism describes above, we believe that waiting for $f + 1$ matching digest for all AFT Map-Tasks before starting the Reduce-Phase can worsen the time for the job completion, especially when WPs arbitrary failures are uncommon. Remember that, assuming that we have $n$ WPGs, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies; all Map-Phase may require long time due, for instance, to network traffic or big  data-set.

A way to increase system's performance reducing its response time is the following: when all $n$ scheduled AFT Map-Tasks have received the \textit{first} replica's result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finish. Essentially, our system make a bet according to which arbitrary faults are highly unlikely therefore first Map-Task replies are considered as correct. This mechanism is known in literature called \textit{Speculative Execution}, an optimization technique applied frequently in computer technology.

Obviously validate the correctness of first Map-Task replies is critical otherwise job's output can be incorrect. To do that, all scheduled AFT Map-Tasks keep on waiting their $f + 1$ matching replies even when Reduce-Phase is started. When Map-Phase is fully finish, if is detected that the input used in the Reduce-Phase was not correct, Reduce-Phase will be restarted with the correct input, otherwise we can finish our job in much less time.

@@

\subsection{Data-Locality-Aware Reduce Scheduling and Shuffle}

So far we have not yet mentioned the shuffle task according to which WP redistribute data (produced by the map function), such that all data belonging to one key is located on the same WP's node. Unlike Hadoop implementation, shuffle task is difficult and expensive due to process replication and to optimization technique described so far. Clearly, due to process replication, data transfers among servers are replicated too, generating an huge amount of network traffic. Evidently, when large data set are involved, move data repeatedly among server became a bottleneck.

Therefore we have adopted a design aware of data locations capable to reduce the overall amount of transferred data: this approach is called \textit{Data-Locality-Aware Reduce Scheduling}. That solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}"; in other words  "\textit{moving computation towards data is cheaper than moving data towards computation}".

Using the same Hadoop terminology, map task output, produces by every WPs, are called \textit{partition} and, contrary to splits, they are of variable sizes: so why not just shuffle smaller partitions instead big one? Then, why not schedule a AFT-Reduce Task to the WPG which nodes has bigger partition? In this way we can avoid transferring huge amount of data increasing overall system performances.

To explain how our scheduler works, let's illustrate an example: assume for simplicity to have only two WPGs $\lbrace g_1, g_2 \rbrace$. Let $P_{i:g_i}$ the partition owned by WPG $g_i$ which contains all key-value pairs which must be submitted to reduce task $R_i$. Suppose that $P_{1:g_1}$, $P_{2:g_1}$, $P_{1:g_2}$ and $P_{2:g_2}$ have a size of 300 MB, 150 MB, 150 MB and 300 MB respectively. In this context LPP schedules $R_1$ to $g_1$ and $R_2$ to $g_2$ because in this way is able to reduce transferred data among WPGs by 50\%. In other words, LPP is design to schedule AFT-Reduce Tasks reducing overall amount of shuffled data.
